\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{graphicx}

\titleformat{\section}{\large\bfseries\color{blue}}{}{0pt}{}
\titlespacing{\section}{0pt}{10pt}{5pt}

\begin{document}

\begin{center}
    {\Huge \textbf{Kirti}} \\
    \vspace{5pt}
    \small \textit{Aspiring Software Engineer | Tech Enthusiast} \\
    \vspace{5pt}
    \textbf{Email:} kirti123x@gmail.com\\  \textbf{GitHub:} \href{https://github.com/Kirti123x}{github.com/Kirti123x}\\   \textbf{LinkedIn:} \href{https://www.linkedin.com/in/kirti-382396310}{linkedin.com/in/kirti-382396310}\\  \textbf{LeetCode:} \href{https://leetcode.com/u/Kirti123x/}{leetcode.com/u/Kirti123x}\\ 
\end{center}

\section*{Education}
\hline
\vspace{5pt}
\textbf{Bachelor of Technology in Computer Science} \hfill 2028 \\
National Institute of Technology, Kurukshetra

\section*{Technical Skills}
\hline
\vspace{5pt}
\textbf{Programming:} Python, C++ \\
\textbf{  Web Technologies:} HTML, CSS, React, Node.js\\

\section*{Experience}
\hline
\vspace{5pt}
\begin{itemize}[leftmargin=10pt]
    \item Developed and optimized RESTful APIs using Node.js and Express.
    \item Improved database query efficiency, reducing response time by 30%.
    \item Collaborated with a team of 5 engineers to build a feature-rich web application.
\end{itemize}

\section*{Projects}
\hline
\vspace{5pt}
\textbf{Personal Portfolio Website} \hfill GitHub: \href{https://github.com/Kirti123x}{github.com/Kirti123x} \\
\begin{itemize}[leftmargin=10pt]
    \item Designed a responsive personal portfolio using React and Tailwind CSS.
    \item Integrated a contact form with Firebase for real-time messaging.
\end{itemize}

\textbf{Amazon Clone (Frontend)} \hfill GitHub: \href{https://github.com/Kirti123x}{github.com/Kirti123x} \\
\begin{itemize}[leftmargin=10pt]
    \item Developed a fully responsive Amazon clone using React.js and Tailwind CSS.
    \item Implemented product listings, shopping cart functionality, and a user-friendly UI.
\end{itemize}

\section*{Leadership and Activities}
\hline
\vspace{5pt}
\textbf{Tech Club Member} \hfill NIT Kurukshetra \\
\begin{itemize}[leftmargin=10pt]
    \item Participated in coding workshops and hackathons.
    \item Engaged in tech talks and networking events.
\end{itemize}

\section*{Certifications}
\hline
\vspace{5pt}
\begin{itemize}[leftmargin=10pt]
    \item Hackathon \hfill 2025
    \item Google Data Analytics Certificate \hfill 2025
\end{itemize}

\section*{Availability}
\hline
\vspace{5pt}
\begin{center}
    \textbf{Available for Summer 2024 Tech Internships | Open to Remote and On-Site Roles}
\end{center}

\end{document}
